Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-09 reports/manuscript.Rmd
Address additional comments

abstract: |
  Children's engagement in screen time is a complex issue.
  While some forms of screen time have consistently been associated with harm, others have been associated with gains, making it difficult to weigh the risks and benefits of use.
  In this umbrella review, we systematically collate and examined meta-analyses examining the effects of screen use on children and youth.
  We converted results onto a common metric (Pearson's r) to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
  These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
  When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potential harm on learning, literacy, body composition, and depression.
  Like-wise, social media was consistently associated with risks to health, with no identified benefits.
  However, we also found that these harms could often be mitigated by certain kinds of content (e.g., educational), or by modifying the context (e.g., co-viewing with a parent).
  In summary, our findings point to the need for careful and nuanced guidelines that support parents to make the best decisions for their children.

@@

While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom&trade;) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
With concerns over the impact of screen use including education, health, social development, and psychological well-being, a broad overview that identifies potential benefits and risks is needed.

@@

In 2016, the American Academy of Pediatrics used a narrative review to examine the benefits and risks of children and adolescents' electronic media [@chassiakosChildrenAdolescentsDigital2016] as a basis for updating their guidelines about screen use [@AAPMediaUseSchoolAged2016].
Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
While there have been other overviews of reviews on screen time, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
<span id = "r1_2">No review has yet examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span>

In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
This review synthesises evidence on any outcome of electronic media exposure.
Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children’s lives.
By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.

@@

*Population*: 
To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
<span id = "r3_5">We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was < 18 years).
A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
We excluded meta-analyses that only contained evidence gathered from adults (age >18 years). </span>

@@

*Publications*: 
We included meta-analyses (or meta-regressions) of quantitative evidence.
To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
For our purposes, a systematic review was one in which the authors attempted to acquire all the research evidence that pertained to their research question(s).
We excluded meta-analyses that did not attempt to summarise all the available evidence (e.g., a meta-analysis of all studies from one laboratory).
We included meta-analyses regardless of the study designs included in the review (e.g., laboratory-based experimental studies, randomised controlled trials, non-randomised controlled trials, longitudinal, cross-sectional, case studies), as long as the studies in the review collected quantitative evidence.
We excluded systematic reviews of qualitative evidence.
We did not formulate inclusion/exclusion criteria related to the risk of bias of the review.
We did, however, employ a risk of bias tool to help interpret the results.
We included full-text, peer-reviewed meta-analyses published or ‘in-press’ in English.
We excluded conference abstracts and meta-analyses that were unpublished.

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table 1).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

<span id ="r2_17">Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
We excluded effect sizes which were reported as relative risk ratios, as meta-analyses did not contain sufficient information to meaningfully convert.
We also excluded effect size estimates when the authors did not provide a sample size.
Where possible, we also extracted effect sizes from the primary studies included in each meta-analysis.

To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
Effect sizes on the original metric are provided in Supplementary File 2.</span>

@@

<span id = "r3_8">After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
In instances where effect sizes from the same combination of exposure and outcome were drawn from different populations (e.g., children vs adolescents) we retained both estimates in our dataset.
</span>

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 4 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
In `r manuscript_info$freq_combos$n1` cases there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table 1.
<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

@@

Screen use research is extensive, varied, and rapidly growing.
Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
Fewer than 20\% of the effects identified met our criteria for statistical credibility.
Most studies which did not meet our critiera failed to provide study-level data (or did not provide sufficent data, such as including effect estimates but not sample sizes).
Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.

@@

<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship.
Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].</span>
<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>

>>>>

abstract: |
  Children's engagement in screen time is a complex issue.
  While some forms of screen time have consistently been associated with harm, others have been associated with gains, making it difficult to weigh the risks and benefits of use.
  In this umbrella review, we systematically collate and examined meta-analyses examining the effects of screen use on children and youth.
  We converted results onto a common metric (Pearson's r) to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_combos` unique combinations of exposures and outcomes.
  If duplicate effect sizes from the same combination of exposure and outcome were drawn from different age groups or study designs we retained them, otherwise we chose the effect size with the largest total sample size.
  We removed effect sizes that could not be harmonized, resulting in `r targets::tar_read(manuscript_info)$unique_effects` from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
  These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
  When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potential harm on learning, literacy, body composition, and depression.
  Like-wise, social media was consistently associated with risks to health, with no identified benefits.
  However, we also found that these harms could often be mitigated by certain kinds of content (e.g., educational), or by modifying the context (e.g., co-viewing with a parent).
  In summary, our findings point to the need for careful and nuanced guidelines that support parents to make the best decisions for their children.

@@

While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom&trade;) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
With concerns over the impact of screen use including education, health, social development, and psychological well-being, an overview that identifies potential benefits and risks is needed.

@@

In 2016, the American Academy of Pediatrics used a narrative review to examine the benefits and risks of children and adolescents' electronic media [@chassiakosChildrenAdolescentsDigital2016] as a basis for updating their guidelines about screen use [@AAPMediaUseSchoolAged2016].
Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
<span id = "r2_9">
While there have been other overviews of reviews on screen time, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
<span id = "r1_2">No review has yet examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span></span>

In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
<span id = "r2_6">This review synthesises evidence on any outcome of electronic media exposure.
We deliberately do not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.</span>

@@

*Population*: 
To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
<span id = "r3_5">We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was < 18 years).
A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).</span>

@@

*Publications*: 
We included meta-analyses (or meta-regressions) of quantitative evidence.
To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
For our purposes, a systematic review was one in which the authors attempted to acquire all the research evidence that pertained to their research question(s).
We excluded meta-analyses that did not attempt to summarise all the available evidence (e.g., a meta-analysis of all studies from one laboratory).
We included meta-analyses regardless of the study designs included in the review (e.g., laboratory-based experimental studies, randomised controlled trials, non-randomised controlled trials, longitudinal, cross-sectional, case studies), as long as the studies in the review collected quantitative evidence.
We excluded systematic reviews of qualitative evidence.
We did not formulate inclusion/exclusion criteria related to the risk of bias of the review.
We did, however, employ a risk of bias tool to help interpret the results.
We included full-text, peer-reviewed meta-analyses published or 'in-press' in English.
We excluded conference abstracts and meta-analyses that were unpublished.

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table 1).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

<span id ="r2_17">Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
We excluded effect sizes which were reported as relative risk ratios or odds ratios, as meta-analyses did not contain sufficient information to meaningfully convert to a correlation.
We also excluded effect size estimates when the authors did not provide a sample size.
Where possible, we also extracted effect sizes from the primary studies included in each meta-analysis.

To facilitate comparisons, we converted effect sizes to Pearson's $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
Effect sizes on the original metric are provided in Supplementary File 2.</span>
<span id ="r2_27">Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines [@funderEvaluatingEffectSize2019]: very small (0.05 < r <= 0.1), small (0.1 < r <= 0.2), medium (0.2 < r <= 0.2), large (0.3 < r <= 0.4), and very large (r >= 0.4).
These are similar to other interpretations based on empircal data [@gignacEffectSizeGuidelines2016].</span>

@@

<span id = "r3_8">After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
In instances where effect sizes from the same combination of exposure and outcome were drawn from different age-groups (e.g., children vs adolescents), or were drawn using different study designs (e.g., cross-sectional vs longitudinal) we retained both estimates in our dataset.
</span>

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 4 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occured in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table 1.</span>
<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

@@

Screen use research is extensive, varied, and rapidly growing.
Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
<span id = "r2_29">Fewer than 20\% of the effects identified met our criteria for statistical credibility.
Most studies which did not meet our critiera failed to provide study-level data (or did not provide sufficent data, such as including effect estimates but not sample sizes).
Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.<span>

@@

<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship.
Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].
Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
Care is needed, therefore, when interpreting the effect sizes.</span>
<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>

### 2023-03-09 reports/revision_letter.Rmd
Address additional comments

output            : revise::letter.pdf
---

@@

@@

@@

@@

@@

@@

@@

@@

\WorkInProgress
\todo{Havea added to table 1. Should we indicate on forest plots?}

@@

\WorkInProgress
\todo{We cite a paper in the protocol on this.}

@@

@@

1. \todo{I don't really want to add this - I think tables of counts are dumb. Thoughts?}
2. \todo{Yes, we should not have used the term "cases". Clear this up}
3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
We have included all of this information in the supplementary file.

@@

\WorkInProgress
\todo{I think this is misleading. It differs by field, outcome, etc.}

@@

1. \todo{Argue not subjective (pre-specified, objective), and we say in limitations that others might choose other options}
2. \todo{Agree - we pre-specified our approaching thinking that it balanced the need to be conservative with the need to be inclusive. But, many effects fail this (fairly low) bar. Add more on this to the discussion.}
3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric, it would not be possible to make any comparisons between the effect sizes.

\todo{Add more to discussion about interpreting sizes carefully.}

@@

@@

@@

\todo{I kind of want to say "also those reviews are probably bad anyway, because it's not hard to put data in forest plots", but I'm not sure there's a professional way to say that.}

@@

We agree that study design should have been a larger factor when choosing which effects to use.

We note that while limiting to certain study designs may improve the quality of the evidence, we are simply summarising what previous reviews have done.
that is, if previous reviews have not limited their evidence to certain designs (or moderated by design), we do not have that information to present.
We also found that there were not a lot of reviews which examined the same exposure and outcome, but differed on choice of study design.
When we included study design as part of our method of choosing effects, it only increased the number of effects by 5 (from 241 to 246).
That is, there are not a lot of instances where the same exposure and outcome are examined in different study designs.

\WorkInProgress
\todo{include study design in the forest plots?}

@@

@@

Yes, we agree that this information is important.
We have included information about the sample in Table 1.
We also note that our criteria for choosing effect sizes in the case of duplicates (i.e., taking the one with the largest N) meant that we would generally take the effect size for the 'typical' population.
More concretely: in the example cited we would typically choose the effect size of television watching on learning for the general population, rather than for those who are depressed, because the sample size would be larger for the former.

\todo{should 'clinical pops' be indicated in the forest plots?}

>>>>

output            : revise::letter.pdf
header-includes:
    - \usepackage[utf8x]{inputenc}
---

@@

Please see our response to Reviewer 2, in particular \comment{r2_29}.
The reviewer raised some important concerns, especially regarding odds ratios which we have decided should not have been included.
For the other issues, we have provided stronger justification for our decisions.

@@

We have revised the introduction with new papers, with a particular focus on other umbrella reviews.

@@

\todo{I'm open to suggestions for what to include here}

One of the key strengths of our review is that it summarises what is available in the literature, rather than trying to *a-priori* predict what areas should be investigated.
That is, our review provides a comprehensive summary of what meta-analytic evidence exists.
We have added some additional text to this effect in the *Introduction*:

`r get_revision("r1_6")`

@@

\todo{Open to suggestions here. I feel like the other changes cover this.}

We feel that we have amply addressed the contribution of this review to the field.
Guidelines should reflect both the most recent evidence, and the most comprehensive evidence.
Many of the previous reviews used to justify guidelines focused on narrow ranges of outcomes (e.g., the impact on adiposity).
We think this is a mistake - you cannot make an informed decision about an action if you only examine the risks, you must also examine potential benefits.

@@

\todo{Open to suggestions here.}

We had difficulty understanding the reviewers exact concern here.
We are happy to revise this further if the reviewer does not feel that the other changes made to the introduction improve the set of arguements.

@@

We have included information on this in our summary of previous umbrella reviews.

`r get_revision("r2_9")`

@@

We agree that "broad approach" does not correctly convey our meaning.
We intended to indicate that in order to make nuanced recommendations, you must have all of the information.
Our approach allowed for a broad set of exposures and outcomes in order to capture all of this information, which is what we intended to convey.
We think our changes elsewhere (see \comment{r1_2} to Reviewer 1, and \comment{r2_6} above) address this.

@@

Yes this is a good suggestion.
We have added a column to indicate if the review was conducted on a general population or not in all of the forest plots.
This information is also available in Table 1.

@@

It's possible the reviewer has misunderstood.
In our original plan, we wrote that $P < 0.001$ would be *one of* the criteria for indicating strong evidence (alongside other metrics, such as sample size and heterogeneity).
We realised that this would restrict our 'strong' evidence to only statistically significant effects.
What would mean that we could not include evidence for no effect as strong evidence, which is clearly a mistake.
Our deviation from the protocol (removing the requirement for a P-value threshold) was intended to rectify this.

@@

1. Yes, we agree that this is confusing.
The use of both 'references' and 'studies' comes from the screening software we used (Covidence; https://www.covidence.org/).
It is intended to capture instances where there are multiple papers ('references') reporting on the same study.
In our case, there were seven instances where a review was conducted but the results of the review were reported in multiple papers.
While we merged these in Covidence for completeness, in all seven cases all of the information that we needed could be retrieved from just one of the papers (which is the one we provide the citation to).
To make this clearer for readers, we've removed this confusing additional extra information.
2. Yes, we agree.
We've collapsed all of the "wrong exposure" codings together.
3. We originally used these when screening full-texts for those where the inclusion criteria targeted the wrong population (e.g., the exclusion criteria was >18 years; coded as "wrong population") vs those where the inclusion criteria included youth, but none of the meta-analytic results could be used because they included adults.
We think for most readers this is an unimportant distinction, and have collapsed these into one category.
We also appreciate the attention to detail.
The updated PRISMA diagram has the correct value in this box.
4. We used sample size as the heuristic for selecting which effect to keep in instances where the same exposure and outcome combination was present, and where the effects represented the same population with the same study designs.
To create a non-subjective method for choosing which effect size to report we chose to use the sample size, under the assumption that the larger study size would provide the most information.
Inspection of the effects that were excluded reveal that this decision is not that impactful: we would have ended up with almost exactly the same set of results had we instead chosen to use the number of included studies (*k*) or the most recent review by publication year.

@@

1. \todo{I don't really want to add this - I don't think it adds much value}
2. We agree that this section was not entirely clear, and we should not have introduced the term 'cases'.
We have revised the language in this section:

`r get_revision("r2_25")`

3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
Most reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
All of the effect sizes (in their original, converted, and recalculated forms) are available in the supplementary material.

@@

We have included this information in the *Methods* section:

`r get_revision("r2_27")`

@@

1. We agree that the our reporting of the method could have been clearer, and have revised the text in this section to more clearly explain our method.
We disagree with the reviewer that the method was "subjective".
If we had multiple effects for the same exposure/outcome combination, and which had the same sample age restrictions and the same study design restrictions, we chose the one with the largest sample size.
We can certainly see how others might use a different method for eliminating duplicate effects (and we state this in the discussion section), but it is difficult to see how using the sample size could be considered "subjective".

2. We were also suprised by the volume of effects which did not meet the criteria for statistical credibility.
We were suprised, for example, that almost a quarter of all effects did not provide study-level data (as might be presented in a forest plot), which we thought would be a low bar to clear.
Almost 40% of those that did have study-level data were derived from samples of less than 1,000 participants (a threshold that has been used by others; 10.1038/s41467-021-24861-8).
And, it seems unwise to place too much emphasis on results where there is an indication of publication bias (i.e., statistically significant Egger's test).
Given that we pre-specified this criteria, we think that it would be inappropriate to lower the standard because the majority of reviews did not reach it.
Instead, we think it reflects the need for the field to raise its standards, especially when it comes to reporting (i.e., making data available, reducing file-drawer problem).

3. We understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
We chose Pearson's *r* as we wanted to focus not on the precise size of the association, but instead on the *direction* and the *magnitude*.
We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric readers would likely still make comparisons, but these would be subjective.
We agree that readers should interpret the effect sizes carefully, and have included text to this effect in the *Discussion*:

@@

We are unclear what the reviewer is referring to here, although we think many of the concerns were addressed in \comment{r2_29}.
We feel that a qualitative sytheses of more than 200 effect sizes is outside the scope of this paper.

@@

Even within recreational screen time, our findings do not support guidelines which focus just on minimisation. 
Video games, for example, are a recreational form of screen time which appear to have some benefits for educational and cognitive outcomes.

@@

@@

We agree that study design should have been a larger factor when choosing which effects to use.
We have rectified this by including study design as a factor in our method of choosing effects.
That is, if there was the same exposure and outcome for the same age group, but one review used cross-sectional evidence and another used longitudinal, we retained both in the dataset.
However, we found that there were not a lot of reviews which examined the same exposure and outcome, but differed on choice of study design.
When we included study design as part of our method of choosing effects, it only increased the number of effects by 5 (from 241 to 246).

We agree that readers should include study design in their interpretation of the results, and have therefore included this information in all forest plots.

@@

\todo{Add a data dictionary}

@@

Yes, we agree that this information is important.
We have included information about the sample in Table 1, and have indicated it on all forest plots.
We also note that our criteria for choosing effect sizes in the case of duplicates (i.e., taking the one with the largest N) meant that we would generally take the effect size for the 'typical' population.
More concretely: in the example cited we would typically choose the effect size of television watching on learning for the general population, rather than for those who are depressed, because the sample size would be larger for the former.
